\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}


    \textbf{\Huge \scshape Stevin George} \\ \vspace{1pt}
    \small 407-257-0293 $|$ \href{mailto:steving2006@gmail.com}{steving2006@gmail.com} $|$ 
    \href{https://linkedin.com/in/georgestevin}{linkedin.com/in/georgestevin} $|$
    \href{https://github.com/StevScripts}{https://github.com/StevScripts}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, FL}
      {B.S. in Computer Science}{May 2028}
    \resumeItem{\textbf{Relevant Coursework:} Computer Science 2, Security in Computing, Object Oriented Programming      
      \textbf{ Organizations}: Knight Hacks (Outreach Member), EXCEL, ACM, Robotics Club (RCCF), GPK}
    \space
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \normalsize{\item{
     \textbf{Languages}{: Java, Python, SQL, TypeScript, JavaScript, Lua, C, HTML/CSS} \\
     \textbf{Frameworks \& Libraries}{: Spring Boot, Flask, Next.js, React, React Native, Node.js, Prisma, Tailwind CSS} \\
     \textbf{Cloud \& DevOps}{: AWS (S3, CloudFront), Docker, Agile, CI/CD, PostgreSQL, Vercel, Git} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Relevant Experience}
  \resumeSubHeadingListStart

\resumeSubheading                           
    {Software Engineering Intern}{May 2026 -- August 2026}
    {PETE Learning}{Orlando, FL}
    \resumeItemListStart                                                                                                                                       
      \resumeItem{Incoming, Working on automations Using N8N automated with coding, programatically makign the automations, building an intelligence corpus for the company, alot of internal tools.}
      
    \resumeItemListEnd                                                                                                                                                                                                                              
                         
  
 \resumeSubheading                           
    {Software Engineer Intern}{Jan. 2026 -- May 2026}
    {Graphics Programming Knights}{Orlando, FL}
    \resumeItemListStart                                                                                                                                                                                                                            
    \resumeItem{Building a club website with \textbf{Next.js} and \textbf{TypeScript} to showcase member projects, gallery posts, and club events for an active student organization.}                                                              
    \resumeItem{Developing a responsive, mobile-first interface using \textbf{Tailwind CSS} and \textbf{Shadcn UI} components, ensuring consistent design and accessibility across all screen sizes.}                                               
    \resumeItem{Designing the site architecture and data models to integrate with a \textbf{PostgreSQL} backend, enabling dynamic rendering of member-submitted projects and event information.}                                                    
  \resumeItemListEnd 
        

%     \resumeSubheading
%       {Software Engineer}{Jan. 2026 -- present}
%       {Society of Asian Scientists and Engineers}{Orlando, FL}
%       \resumeItemListStart
%         \resumeItem{Engineered a {Progressive Web App} using \textbf{Next.js} and \textbf{TailwindCSS} to streamline member attendance tracking and event check-ins.}
%         \resumeItem{Developed asynchronous \textbf{RESTful API} routes to manage real-time data synchronization between the \textbf{React} frontend and a backend database, reducing manual entry errors.}
% \resumeItem{Implemented service workers and manifest configurations to enable \textbf{offline functionality} and a native-like "add-to-home-screen" experience for mobile users.}
%       \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
 \resumeProjectHeading
  {\textbf{Recall} $|$ \emph{Python, Gemini 2.5 Flash, YOLOv8, ChromaDB, ElevenLabs, ESP32, Next.js}}{Mar. 2026}
  \resumeItemListStart
    \resumeItem{Won \textbf{2nd Place} out of 85+ projects at \textbf{HackUSF 2026} by building a \textbf{wearable AI memory assistant} that passively captures a user's environment and enables instant natural language queries}
 \resumeItem{Designed a computer vision pipeline using \textbf{OpenCV} and \textbf{YOLOv8 Nano} to filter video frames, sending scenes to \textbf{Gemini 2.5} Flash Vision to generate detailed spatial descriptions of the user's environment.}
\resumeItem{Indexed scene descriptions in \textbf{SQLite} and \textbf{ChromaDB} vector embeddings for semantic search, surfaced through a \textbf{Flask} API with a live memory timeline and \textbf{ElevenLabs TTS} conversational chat.}
\resumeItemListEnd
  
    \resumeProjectHeading
  {\textbf{TideSense} $|$ \emph{React Native, TypeScript, Python, TensorFlow Lite}}{Nov. 2025}
  \resumeItemListStart
    \resumeItem{Engineered a \textbf{full-stack AI mobile application} that utilizes computer vision to identify and classify dangerous riptide currents via a smartphone camera.}
    \resumeItem{Implemented \textbf{TensorFlow Lite} for on-device object detection, developing a custom post-processing algorithm to filter model noise and improve detection stability.}
    \resumeItem{Integrated the \textbf{Gemini API} to provide contextual safety advice and utilized the \textbf{ElevenLabs API} to generate real-time audio risk assessments for users.}
  \resumeItemListEnd


  
\resumeProjectHeading
  {\textbf{Next Step} $|$ \emph{Next.js, React, TypeScript, Python, Flask}}{Sep. 2025}
  \resumeItemListStart
    \resumeItem{\textbf{3rd Place Winner} (State Farm Challenge) out of 50+ projects at \textbf{ShellHacks 2025} for an AI-driven insurance education platform.}
    \resumeItem{Developed interactive, voice-based simulations using \textbf{Vapi AI} to teach insurance fundamentals through real-time, decision-based scenarios.}
    \resumeItem{Built a scoring system to evaluate user safety and knowledge retention, providing immediate feedback based on simulated insurance claims and coverage choices.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd




\vspace{1.5pt}

\end{document}